Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-21 cav2017/cav2017.tex
completeness threshold goes here?
adding pseudocode

\usepackage{amssymb}
\usepackage{amsmath}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{framed}
\usepackage{listings}

@@

We compute a candidate $K$, with the required controller precision $\langle I_c,F_c\rangle$, that satisfies both the stability criteria detailed in 
section \todo{ref stability section}, and the safety specification in section \todo{ref for safety}.
The stability criteria are satisfied if the characteristic polynomial of $A_d - B_d * K_d$ meets Jury's criteria. This is 
independent of the initial states. 
In order to synthesise a controller for satisfaction of the safety specification, we unwind the transition system
$k$ steps, and pick a controller $K$ and an initial state such that the states at each step do not violate the safety criteria.

@@

@@

\todo[inline]{ALESSANDRO: please write out proof that checking only the corner cases is valid for the safety verification}

@@

 \addtodo{discuss the computation
  of the completeness threshold}

>>>>

\usepackage{amssymb}
\usepackage{amsmath}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{framed}
\usepackage{listings}
\usepackage{algorithm,algpseudocode}

@@

We compute a candidate $K$, with the required controller precision $\langle I_c,F_c\rangle$, that satisfies both the stability criteria detailed in 
section \todo{ref stability section}, and the safety specification in section \todo{ref for safety}.
The stability criteria are satisfied if the characteristic polynomial of $A_d - B_d * K_d$ meets Jury's criteria. This is 
independent of the initial states. 
In order to synthesise a controller for satisfaction of the safety specification, we unwind the transition system
$k$ steps, and pick a controller $K$ and an initial state such that the states at each step do not violate the safety criteria. 
The unwinding calculation includes the conversion from plant precision to the fixed point controller precision.

@@

\begin{algorithm}[]
\begin{algorithmic}[1]
\Function{$safetyCheck()$}{}
	\State assert($ \underline{u}  \leq u \leq \overline{u}$)
	\While{$i=0; i< k; i++$}
		%\State $u = (\langle I_p,F_p\rangle)((\langle I_c,F_c\rangle)K * (\langle I_c,F_c\rangle) x)$
		\State $u = (plant\_typet)((controller\_typet)K * (controller\_typet) x)$
		\State $x = A * x + B * u$
		\State assert($\underline{x} \leq x \leq \overline{x}$ )
  	\EndWhile
  %\State Return $K$
\EndFunction
\end{algorithmic}
\label{alg:safetycheck}
\end{algorithm}

@@

\todo[inline]{Alessandro: please write out proof that checking only the corner cases is valid for the safety verification}

@@

\todo[inline]{Alessandro: please can we have the proof for the completeness threshold here}
\missingfigure{picture for completeness threshold}
